---
title: "midterm"
author: "ssheng6"
output: html_document
---
  
## Midterm.
  
#### 1.  Summarize the planes
  

```{r}
# put your answer here. 
library(tidyverse)
library(nycflights13)
library(dplyr)
library(tidyr)
library(ggplot2)
planes


flight1 = flights %>%
  group_by(tailnum) %>%
  summarise(mean_delay=mean(arr_delay,na.rm=TRUE))

flight2 = flights %>%
  group_by(tailnum) %>%
  summarise(mean_distance=mean(distance,na.rm=TRUE))
flight2

flight3 = flights%>%
  group_by(tailnum) %>%
  summarise(n=n())
flight3

p1 = planes %>%
  left_join(flight1, c("tailnum" = "tailnum"))
p1 
  
p2 = p1 %>%
  left_join(flight2, c("tailnum" = "tailnum"))
p2



p2 %>% ggplot(aes( mean_distance,mean_delay))+geom_point() 


p3 = p2 %>%
  left_join(flight3, c("tailnum" = "tailnum"))

p3 %>% ggplot(aes(n,mean_delay))+geom_point() 

p3 %>% ggplot(aes(year,mean_delay))+geom_point() 

```

#### 2.   Distance vs flight time

2a) Let's only study flights departing from EWR. For each destination, compute the average flight time (air_time) and the number of miles to that destination.  Make a plot with miles to destination on the horizontal axis and average flight time on the vertical axis.    

```{r}


 
```


2b) Using this data, compute the distance divided by the average air_time.  Call this the typical_speed.  Plot the typical_speed on the vertical axis and distance on the horizontal axis.  

```{r}



 
```

#### 3.   Bad weather metric

Let's fit a linear model, for each origin x day.  The outcome is the proportion of flights canceled.  The features will be simple summaries of the weather.  

I've done a bunch of work below to get you started... there is one line that you need to finish...

```{r}
flights_canceled = 
  flights %>% 
  group_by(origin, month,day) %>% 
  summarise(Y = mean(is.na(dep_time)))

bad_weather = 
  weather %>% 
  group_by(origin, month,day) %>% 
  summarize(temp = mean(temp, na.rm = T),
            dewp = mean(dewp, na.rm = T),
            humid = mean(humid, na.rm = T),
            wind_speed = mean(wind_speed, na.rm = T),
            wind_gust = mean(wind_gust, na.rm = T),
            precip = mean(precip, na.rm = T),
            visib = mean(visib, na.rm = T))

# put these data frames together with a column for Y and columns for all the weather variables.  DON'T OVER THINK THIS!

#X = .....

# then, uncomment these next lines to fit a linear model...
#fit = lm(Y~temp + dewp+humid+wind_speed + wind_gust+precip+visib, data = X)
#summary(fit)       
            
```


#### 4.  Planes with four engines

Find all of the planes with 4 engines:

```{r}


planes%>%
  filter(engines =="4")


 
```



